Illusion Game Validation (Study 1)

### 2022-08-04 study1.Rmd
re-make stimuli

```{r, echo = FALSE, warning=FALSE, message=FALSE}
options(digits = 3,
        mc.cores = 4,
        brms.algorithm = "sampling",
        brms.backend = "cmdstanr")

@@

```{r message=FALSE, warning=FALSE, cache=cache,results='hide'}
# plot(seq(0, 1, length.out=100), seq(0, 1, length.out=100)**(1/3), "l", col="green")
# lines(seq(0, 1, length.out=100), sqrt(seq(0, 1, length.out=100)), "l", col="red")
# lines(seq(0, 1, length.out=100), log(1+seq(0, 1, length.out=100)), "l", col="blue")
# lines(seq(0, 1, length.out=100), seq(0, 1, length.out=100), "l", col="black")

@@

```{r message=FALSE, warning=FALSE, cache=cache}
formula <- brms::bf(
  Error ~ Illusion_Difference_cbrt * Illusion_Strength + 
    (1 | Participant),
  family = "bernoulli"
)

@@

  vars <- insight::find_predictors(model)$conditional
  n_lines <- length(unique(data[[vars[1]]]))
  pred <- estimate_relation(model,
                            at = vars,
                            length = c(NA, 25))
  pred$Illusion_Difference <- as.factor(round(pred[[vars[1]]], 2))

@@

```{r message=FALSE, warning=FALSE, cache=cache,results='hide'}
best_models(data)
```

@@

```{r message=FALSE, warning=FALSE, cache=cache}
formula <- brms::bf(
  Error ~ Illusion_Difference_cbrt * Illusion_Strength + 
    (1 | Participant),
  family = "bernoulli"
)

@@

```{r message=FALSE, warning=FALSE, cache=cache}
formula <- brms::bf(
  Error ~ log(Illusion_Difference) * Illusion_Strength + 
    (1 | Participant),
  family = "bernoulli"
)

@@

@@

```{r message=FALSE, warning=FALSE, cache=cache}
formula <- brms::bf(
  Error ~ log(Illusion_Difference) * Illusion_Strength + 
    (1 | Participant),
  family = "bernoulli"
)

@@

>>>>

```{r, echo = FALSE, warning=FALSE, message=FALSE}
options(digits = 3,
        mc.cores = 4,
        brms.algorithm = "meanfield",
        brms.backend = "cmdstanr")

@@

```{r message=FALSE, warning=FALSE, cache=cache}
# plot(seq(0, 1, length.out=100), seq(0, 1, length.out=100)**(1/3), "l", col="green")
# lines(seq(0, 1, length.out=100), sqrt(seq(0, 1, length.out=100)), "l", col="red")
# lines(seq(0, 1, length.out=100), log(1+seq(0, 1, length.out=100)), "l", col="blue")
# lines(seq(0, 1, length.out=100), seq(0, 1, length.out=100), "l", col="black")

@@

```{r message=FALSE, warning=FALSE, cache=cache}
cbrt <- function(x) sign(x) * abs(x)^(1/3)

formula <- brms::bf(
  Error ~ poly(Illusion_Difference, 2) * Illusion_Strength + 
    (1 | Participant),
  family = "bernoulli"
)

@@

  # Get variables
  vars <- insight::find_predictors(model)$conditional
  vardiff <- vars[1]
  varstrength <- vars[2]

  n_lines <- length(unique(data[[vardiff]]))
  pred <- estimate_relation(model,
                            at = vars,
                            length = c(NA, 25))
  pred$Illusion_Difference <- as.factor(round(pred[[vardiff]], 2))

@@

@@

```{r message=FALSE, warning=FALSE, cache=cache}
formula <- brms::bf(
  Error ~ poly(Illusion_Difference, 2) * Illusion_Strength + 
    (1 | Participant),
  family = "bernoulli"
)

@@

```{r message=FALSE, warning=FALSE, cache=cache}
formula <- brms::bf(
  Error ~ poly(Illusion_Difference, 2) * poly(Illusion_Strength, 2) + 
    (1 | Participant),
  family = "bernoulli"
)

@@

```{r message=FALSE, warning=FALSE, cache=cache}
formula <- brms::bf(
  Error ~ sqrt(Illusion_Difference) * Illusion_Strength + 
    (1 | Participant),
  family = "bernoulli"
)

@@

```{r message=FALSE, warning=FALSE, cache=cache}
formula <- brms::bf(
  Error ~ poly(Illusion_Difference, 2) * Illusion_Strength + 
    (1 | Participant),
  family = "bernoulli"
)

@@

```{r message=FALSE, warning=FALSE, cache=cache}
formula <- brms::bf(
  Error ~ poly(Illusion_Difference, 2) * poly(Illusion_Strength, 2) + 
    (1 | Participant),
  family = "bernoulli"
)
